### 2011-06-19 manuscript.tex
Fix quote style and add latex scaffolding.

"... escape velocity?  It's too much ..." the woman's voice had said.

Jesse stopped, wheeling around to find the voice, but it was lost in the groggy brook of sounds and suitcoats moving toward him, away from him, and breaking around him.  He had just been thinking about his job and remembering his mother's advice.  /When you're stuck but ambition pulls you up, use it, you're already at escape velocity/... .  A tall passerby bumped into him, sending a momentary pain through his neck and shoulders.  The stranger apologized and tipped his hat, quickly regaining his brisk walking pace.

/Nobody else's mother teaches life lessons with physics metaphores/, he thought, allowing himself a wry smile.  He looked across Bedford Avenue, took a deep breath, and stepped back into the stream of Brooklyners.

@@

"Sascha, the top feed is ready," called a voice near the window.  The Office of Internal Affairs, despite the lofty title, was a cramped, stuffy office that contained five desks, eighteen computers and other office machines, and could comfortably fit three bodies, provided that the bodies were reasonably proportioned and were not given to clumsiness.  Sascha sat facing the north wall, preferring not to be distracted by the constant movement of his colleagues.  Jill, the office technology specialist, sat near the windows where she could keep a watchful eye on the myriad devices that kept the room warm.  Sean, the interdepartmental liason (the External Internal Affairs Spokesman, Sascha called him), worked at a stand-up desk that was mounted on the west wall between the two oat doors.  The remainder of the 600 square foot space was a labyrinth of machines, cables clamped to the floor with black duct tape, stacks of official university records, and the occasional abandoned coffee mug.  The abundance of machines meant that one window propped open year-around.

"Got it."  Sascha stretched his shoulders and called up the day's list of business items that had been assembled by the administrative assistants on the floor above.  Amazing that these lists ever get out the door.  Sascha knew that despite the polished look of the top feed, it was the result of hours of messy negotiations, hearsay, and petty politics.  If the students only knew what they were paying for, he thought.

@@

Scanning through the list, Sascha spotted a familiar name.  He took a drink from his coffee mug, taking a moment to process the news.

"Jill, did you see that Winter is on the list again?" he said, his eyes still on the computer screen.

"Hadn't noticed.  What's the claim?" Jill asked.

"Espionage and destruction of university property," Sasched said, his voice laced with disbelief.

Sascha heard the steady rhythm of Jill's typing stop abruptly.  He turned to face her.  "This isn't his first time on the feed, but it sounds like it could be his last.  And I'd bet my left nut that he's innocent."

Jill ignored the comment.  "I'll admit that espionage is over the top, even for this group of suits.  Winter's first time was inconclusive, though, and you have to admit that it was fishy.

"Fishy or not, the guy has a good moral compass.  He's innocent."

@@

								* * *

Jesse swallowed hard, wondering how he had gotten here.  The university's prosecutor had just painted him as a screwoff that, even though he should never have been hired, /most definitely/ should not be allowed to handle anything more than a press release for an obscure bit of undergraduate research.  Jesse had admired the bastard's poise and confidence as he delivered one gently stretched fact after another, building to a rousing conclusion that even Jesse found convincing but didn't agree with reality.  /Never let the facts get in the way/, Jesse thought to himself.

Three weeks earlier, Jesse had just finished writing a report for his superiors that evaluated the success of a new program at CUNY that paired journalism students with investigative reporters from major news organizations and private investigative agencies.  William Tweedie, the current president of CUNY, had made it his personal mission to restore investigative journalism to its rightful place as a tool that feeds the beating heart of democracy.  In addition to the partnership with private agencies, the vision stated, students would conduct an internship overseas in an area of strategic interest to the United States.  Military zones and several unfriendly nations were understandable excluded, but this did nothing to blunt the flood of criticism that the Tweedie, and the university as a whole, endured in the months that followed.

@@

Tweedie refused to pull the plug on the program that had made him a household name.  Perhaps by taking public figures to task and embracing modern technology as a means of tracking and eliminating corruption, he argued, the young public can wrest control of its future from the cash-heavy organizations that have a key vested interest in keeping everyone in the dark.  It took a toll on him, which was evidenced most clearly by the private security detail that he hired to keep a few eyes on his family's small house.  His efforts to promote investigative journalism and to encourage students to take up the fight inspired many, especially students in France and elsewhere in the United States, to form impromptu groups of vigilanti reporters.  There were nearly reports of students being arrested or harrassed by police after they had been found trespassing or had been accused of stalking.  While the actions of these student reporters departed from what Tweedie had intended, it told him something important: the will to peel back the layers of secrecy and deceit that crippled the public's understanding of major events, long thought to be lost on the young generations of the 21st century, was alive and well.

@@

When William Tweedie had announced his pet program for reinvigorating investigative journalism, he had personally notified Jesse that his job description would be changing.  If he felt comfortable with the plan, then he was welcome to stay.  Jesse was intrigued by the promise of hush-hush work, additional travel, and doing his part to promote an old component of journalism that he had found lacking.  He signed a non-disclosure agreement, agreed to the revised terms, and came to work the next week to find that his desk and computer had been removed.  In its place was a note from the dean and a plane ticket without a marked destination that left from a terminal at JFK that Jesse had  never heard of.  "This should be educational," he said, turning on his heel and heading toward the elevator.

"You're going to eastern Europe," the dean had told him.  "The flight plan has been filed, and your pilot knows what to do.  Here's some background for you to read over while you're over the Atlantic."  He handed Jesse a thin tablet computer whose only marking was a serial number etched into the upper right corner.

"What's the scoop?" Jesse asked, running his hand over the tablet.

"You'll find everything on there," said the dean.  "This project is the president's baby, and you probably know more than I do.  When you land, use the switch on the side of the tablet to securely erase its flash memory.  None of the information on it is illegal, but it's sensitive and we don't want you getting tied up in a rumble with immigration."

"All right," Jesse said.  He noted the location of the secure erasure switch and looked back at the dean.  "Should I pay an extra month's rent, or is this a visit for tea?"

The dean laughed.  "See you in two weeks, son."

					* * *

@@

"Don't worry, the bottoms are magnetic," Milssen said, gently tipping his own mug from side to side to show the resistance of the magnet.  "One of the perks of these corporate birds."

@@

"Ready for duty?" Milssen asked with a smile.

"Not a chance," Jesse said, "but I'll do what I can.  These kids really stepped in it."

"The bits of news that have made it to my ear haven't been good.  Be careful, and we'll see you Thursday evening.  Give me a call when you're packed up.  We'll be starting our descent in about twenty."

@@

Jesse knew that tomorrow, Wednesday, would be a tense affair.  He kept his nerves hidden, but his bowels never got the memo.  /I won't be doing this until I retire, unless they let me go at 32/, he thought, looking out the tiny window at the hills of central Europe.

The kids had /really/ stepped in it.  One student, the son of Polish immigrants, had enrolled in the new investigative journalism program at CUNY with a personal mission to prove that his father's failed bid for a seat on the Warsaw City Council in 1986.  The family was convinced that an opponent had floated a rumor about his father's marital fidelity shortly before the election, and that another political rival had abused her position of power at town meetings as a soapbox for making inaccurate statements about the family's intentions.  The student, Sam Rzeznik, had recruited two of his classmates to join him in Poland for a month to investigate the case.

The true story, however, had only come to light after the team of students was arrested by Interpol for breaking into the offices of a local political party and installing recording devices.  The official application for funds had stated that the team would be investigating instances of polling irregularities at a handful of small voting precincts outside of Warsaw.  The low-key nature of the trip, and the delicate issue at hand, had won over the review board and brought praise from William Tweedie.  The team had been awarded a travel and research grant for $8,000, enough to keep them fed and mobile for 30 days.

@@

									* * *

@@

"Jesse Winter?" the man said.  His voice was clear despite an accent that Jesse couldn't place, but the accent didn't concern him as much as the lack of friendliness.  Jesse reminded himself that he shouldn't expect to make friends today.  /Time to go to work/.

"Pleased to meet you.  Mr...?" Jesse said, offering his hand.

The man stood up, shaking Jesse's hand.  "Jasna.  Marcel Jasna.  You can call me Marcel.  May I call you Jesse?"

"Sure," Jesse said.

"Shall we sit, then?" said Marcel, gesturing to the empty chair across the small table.

@@

"Well, Jesse, it's no secret why we come here today," Marcel said simply.  "The manager of my brother's political office caught your students in his building.  It was clear to us that they were spying on our meetings and attempting to sabotage our campaign.  We have video and audio evidence from the night when they entered the building and left recording devices.  This is, as you say, an open and shut case, don't you think?"

Jesse opened his mouth to respond, but Marcel had paused only for rhetorical effect.  He went on: "My brother has no interest in ruining the lives of young people.  But he finds your program that encourages students to become foreign spies for the United States to be distasteful and shameful.  If students go to jail for a time in order to bring the proper shame on your program, very few Polish citizens here will pay attention.  Your program is unpopular in your own country, yes?"

This time Marcel stopped to wait for a response, but Jesse sensed a trap.  "The program enjoys strong support from many quarters," he offered.

"Yes, there are always those who see public servants as corrupt by definition.  Have you noticed that foreign politicians are always corrupt, but your government does not look at its own face in a mirror?"  Marcel took a drink from his glass, then cleared his throat.  "This is not so simple as you think, Jesse.  You are thinking of your students, their future, their families, your president, perhaps your job.  We understand that it is far deeper.  Each time our politicians are painted as corrupt, Poland suffers.  We have suffered under the heel of such injustice for most of a century."

Jesse shifted in his seat.  "Marcel, these students lied to us.  I understand your position on spying, and I know that from your vantage point we seem to be training a new crop of young spies.  You need to know that these students were not authorized to conduct themselves in this way.  They lied on the application, and they lied to the review committee."

"This does not change substance of the situation."

"That's correct.  But it changes the details of the situation that you and I care about.  We're not here to debate state philosophies on espionage.  This is about the welfare of a group of kids who, while they showed themselves to be overzealous, have passion and talent that /must/ be put to productive uses.  Do you see?"

Marcel responded immediately.  "With respect, the fate of the students is beside the point.  This is an issue of national and political sovereignty, and we intend to treat it as such.  I must admit that I do not think we will reach a settlement.  We must not appear weak in the face of interference from America, even if the face is that of a young spy ring."

@@

"Our university is prepared to work with you, sir," Jesse continued.  We have no interest in inflaming the relationship between the U.S. and a friendly nation such as Poland.  We know that despite your feelings about espionage, it would not bode well for your campaign to be associated with the arrest of a Polish student."  Turning his palms upward in a conciliatory gesture, Jesse added, "What options remain on the table?"

Marcel leaned back in his seat and tilted his head to the right, clearly wondering what Jesse had been in Jesse's mind as he spoke those words.  It was a moment before he spoke again.  "You offer us money, Jesse?"

"We are prepared to cover the costs of the repairs to your brother's office, as well as any legal costs that you've absorbed.  Beyond that, well... this is a negotiation."

"Please excuse me for a moment, Jesse," Marcel said, rising to his feet and walking toward the back door of the cafe.

/Time for a conference during the powwow/, Jesse thought to himself.  He took the moment to enjoy a taste of the gin and tonic in front of him that had so far been ignored.  As the strong flavor filled his senses, Jesse talked himself through the next few minutes of his conversation.  The man in the other chair suspected that Jesse was out of chips in the negotiation.  Jesse was certain of that.  Jesse also knew that his own case was weak and that offering money for repairs and cooperation was small potatoes to these guys.  Someone who cares about national and political sovereignty wasn't going to let a group of foreign kids with an agenda go without making a point or making some demands to make the American politians squirm.  And Jesse was just a pawn in all of this.  He knew that Marcel felt no personal sympathy for him.

@@

"My apologies, Jesse," Marcel said as he took his seat.  "My brother can be very detailed."

"Not to worry.  How is he doing?"

"Very busy these days.  This issue with the students has taken a lot of his time, and he is eager to wash his hands of them."

/Didn't expect that/, Jesse thought.  /But he's not finished/.

"However," Marcel said, leaning back in his seat and slowly turning his glass, "a detail has come to his attention today.  One of the students, Sam Rzeznik.  You know of him?"

@@

"Yes.  It seems that his family has a history.  A history that complicates things for us.  What do you know about this?"

"I know that Sam is of Polish descent.  He mentioned in his interview with our review board that his grandfather was a public servant, but no serious problems came up during the proceedings.  Everything that Sam told us was verified before he was allowed to start his research project."

That much was true, but Jesse wasn't revealing his hand just yet.  The political problems had not involved Sam's grandfather, who had been involved in municipal government for most of his life.  Sam's father, on the other hand, had found himself the victim of circumstances entirely beyond his control.  The review board that CUNY had convened to consider the applications submitted by the investigate journalism students had learned about Jesse's father's political past after conversing with Polish authorities, but the board had given its stamp of approval after reviewing the facts.

"Yes, his grandfather served in the city government with my grandfather.  Those were very good days for Poland, despite the problems of the world.  It was the next generation that began the divisive era of our politics that we still see today.  The dishonesty.  The posturing."  Marcel paused, looking pointedly at Jesse.  "And the /spying/.  It is this generation that Sam's father helped to assemble.

"My father in his third year on the city council when Sam's father declared himself a candidate for the same seat.  My father had worked for ten years to clean up this city, and to restore pride to Warsaw citizens.  He had done every task to match the letter of the law.  His contituents trusted him.  Sent him letters of thanks each year.  He knew the spirit of the people, and knew how to bring money and business to Warsaw.  He understood the real purpose of a public life."

Marcel took a deep breath, clearly incensed by the memories that he was bringing to mind.  "When Sam's father declared himself a candidate, he... he knew nothing of politics.  He knew nothing of campaigns.  His only public achievement was to manage the local library, and poorly at that.  The library was never lower on funds.  He began to attend city council meetings, asking impossible questions.  There was neven a more irritating man.  He knew nothing of the business of government, but he made it his mission to lecture everyone on what he called the 'proper order of the gathering'.

"It was known that he saw visited women other than his wife.  After he declared his candidacy, this secret became known to the public.  It is not clear how this information became known.  He never recovered from the stain on his reputation, and he lost the election.  It was soon after that his family left the country, and we see now that he reaches through his son in an attempt to blame us for his past mistakes."

Marcel paused to finish his scotch.  "There will be no deal, Jesse."

"Are you familiar with the phrase 'catch-22', Marcel?"

"Yes, of course.  It is a situation in which every available course of action carries negative consequences.  Why do you ask this?"

"Since you are familiar with your father's political story, you might remember an incident involving an old woman in June of 1986."

Marcel's face clouded, and he shifted in his seat.  "Yes," he allowed, "I am familiar."

"If I told you that we had an voice record of that conversation, would this change the substance of our discussion?"

@@

Marcel considered Jesse for a long moment.  "You attempt to deceive me."

"It is not your claims, sir, but the way that you abuse the trust of the people with one hand while smoothing their feathers with the other that make me doubt you," Jesse said, making it clear that he was uttering a quotation.  She spoke with an east Warsaw accent.

Marcel stared at him.  He would have remembered that decades-old quote.  Just when Jesse was sure that he had collected his thoughts and had worked out a stinging train of logic, he took a deep breath and pulled a cash clip from his pocket.  He placed three Euro bills on the table before replacing the clip in his trowsers.  Then he met Jesse's eyes.

"Your students will meet you at the airport tomorrow, Mr. Winter."

Marcel was out of his seat and halfway to the door of the cafe before Jesse fully processed what had happened.  The students were absolved of their legal worries.  An impossible situation had been turned on its head.  But there was no way that this was the end of the story.  These guys didn't quit that easily.  Jesse's trump card had ended the contest, but he knew that he would hear from Marcel again before he retired.  /Unless I retire at 32/.

@@

"Mr. Jesse Winters?" the officer asked, glancing at a sheet of paper in his hand and looking back at Jesse.

"Yes?" Jesse replied.

"I'm detective Morse from the CUNY police department, I'd like to ask you a few questions, if that's all right."

"Certainly.  Please come in."  /This should be good/, Jesse thought, feeling his pulse quicken.

The officer stood near the door, refusing Jesse's offer of a chair.  "Mr. Winter, one of the members of the board of directors has launched an investigation into your involvement in the Warsaw incident from June.  Are you familiar with that case?"

"Yes, I traveled to Poland in June to negotiate on behalf of the university.  What's this about?"

"Would you mind coming down to the station to talk about it?  We can be sure of our privacy there."

"Am I under arrest, detective?"

"No, sir.  We just want you to discuss a few things with us."

"This office is private.  Why not stay here?"  Jesse felt his old privacy hackles starting to rise.  /My office is certainly more private than an interrogation room/.

"With all due respect, Jesse, given your involvement in this case you should know better than to assume something like that."

@@

The case against Jesse was surprisingly weak, but the university prosecutor had constructed an elaborate argument that had a chance of succeeding.  If he could convince the judge that Jesse had issued a threat, even an implied one, then Jesse could be found guilty of obstruction of justice.  His attorney seemed confident that the judge would reject the argument, but its plausibility made Jesse nervous.  If the key question was whether Jesse issued a threat, then he was in a difficult position.  He /had/ issued a threat, although it was not spoken.  Anyone who had been privy to the conversation in Warsaw would have understood that what Jesse said was a threat.  But the thing gnawing at Jesse's mind was how that information had made its way to the ear of one of the board members.  One of two things was true.  Either Rheingold had secured a copy of the documents on the tablet computer that Jesse had carried to Warsaw, or Marcel and his brother had made a contact in the United States.  The latter worried Jesse on a much deeper level than the former.

@@

"Will the defendant please rise?" the judge drawled.

@@

"In the case of Rheingold versus Winter, we find the defendant not guilty on the charges of obstruction of justice.  Mr. Winter, you are free to leave."  After a brief pause, the judge cleared his throat and added: "Off the record, I think that this case was a poor use of the court's time.  Good day, gentlemen."

@@

"Good show, Jesse," Sascha Greene said with a wink.

>>>>

\documentclass[12pt]{book}
\usepackage[paperwidth=5.25in,paperheight=8in,hmargin=0.75in,vmargin=0.5in]{geometry}

% To skip blank pages that make new chapters start on a right-side page
%\makeatletter\@openrightfalse

\begin{document}

\chapter{}

``---escape velocity?  It's too much---'' the woman's voice had said.

Jesse stopped, wheeling around to find the voice, but it was lost in the groggy brook of sounds and suitcoats moving toward him, away from him, and breaking around him.  He had just been thinking about his job and remembering his mother's advice.  \emph{When you're stuck but ambition pulls you up, use it, you're already at escape velocity}\dots.  A short passerby bumped into him, sending a momentary pain through his neck and shoulders.  The stranger apologized and tipped his hat, quickly regaining his brisk walking pace.

\emph{Nobody else's mother teaches life lessons with physics metaphors}, Jesse thought, allowing himself a wry smile.  He looked across Bedford Avenue, took a deep breath, and stepped back into the stream of Brooklyners.

\chapter{}

@@

``Sascha, the top feed is ready,'' called a voice near the window.  The Office of Internal Affairs, despite the lofty title, was a cramped, stuffy office that contained five desks, eighteen computers and other office machines, and could comfortably fit three bodies, provided that the bodies were reasonably proportioned and were not given to clumsiness.  Sascha sat facing the north wall, preferring not to be distracted by the constant movement of his colleagues.  Jill, the office technology specialist, sat near the windows where she could keep a watchful eye on the myriad devices that kept the room warm.  Sean, the interdepartmental liason (the External Internal Affairs Spokesman, Sascha called him), worked at a stand-up desk that was mounted on the west wall between the two oat doors.  The remainder of the 600 square foot space was a labyrinth of machines, cables clamped to the floor with black duct tape, stacks of official university records, and the occasional abandoned coffee mug.  The abundance of machines meant that one window stayed propped open year-around.

``Got it,'' Sascha said.  He stretched his shoulders and called up the day's list of business items that had been assembled by the administrative assistants on the floor above.  \emph{Amazing that these lists ever get out the door\emph{, he thought.  Sascha knew that despite the polished look of the top feed, it was the result of hours of messy negotiations, hearsay, and petty politics.  }If the students only knew what they were paying for}.

@@

Scanning through the list, Sascha spotted a familiar name.  He took a drink from his coffee mug, taking a moment to process the news.  He absently poked the rubber Gumby figure sitting next to his monitor, making it jiggle.

``Jill, did you see that Winter is on the list again?'' he said, his eyes still on the computer screen.

``Hadn't noticed.  What's the claim?'' Jill asked.

``Espionage and destruction of university property,'' Sasched said, his voice laced with disbelief.

Sascha heard the steady rhythm of Jill's typing stop abruptly.  He turned to face her.  ``This isn't his first time on the feed, but it sounds like it could be his last.  And I'd bet my left nut that he's innocent.''

Jill ignored the comment.  ``I'll admit that espionage is over the top, even for this group of suits.  Winter's first time was inconclusive, though, and you have to admit that it was fishy.''

``Fishy or not, the guy has a good moral compass.  He's innocent.''

@@

\chapter{}

Jesse swallowed hard, wondering how he had gotten here.  The university's prosecutor had just painted him as a screwoff that, even though he should never have been hired, \emph{most definitely} should not be allowed to handle anything more than a press release for an obscure bit of undergraduate research.  Jesse had admired the bastard's poise and confidence as he delivered one gently stretched fact after another, building to a rousing conclusion that even Jesse found convincing.  But it simply didn't agree with reality.  \emph{Never let the facts get in the way}, Jesse thought to himself.

Three weeks earlier, Jesse had just finished writing a report for his superiors that evaluated the success of a new program at CUNY that paired journalism students with investigative reporters from major news organizations and private investigative agencies.  William Tweedie, the current president of CUNY, had made it his personal mission to restore investigative journalism to its rightful place as a tool that feeds the beating heart of democracy.  In addition to the partnership with private agencies, the vision stated, students would conduct an internship overseas in an area of strategic interest to the United States.  Military zones and several unfriendly nations were understandably excluded, but this did nothing to blunt the flood of criticism that the Tweedie, and the university as a whole, endured in the months that followed.

@@

Tweedie refused to pull the plug on the program that had made him a household name.  Perhaps by taking public figures to task and embracing modern technology as a means of tracking and eliminating corruption, he argued, the young public can wrest control of its future from the cash-heavy organizations that have a key vested interest in keeping everyone in the dark.  It took a toll on him, which was evidenced most clearly by the private security detail that he hired to keep a few eyes on his family's small house.  His efforts to promote investigative journalism and to encourage students to take up the fight inspired many, especially students in France and elsewhere in the United States, to form impromptu groups of vigilante reporters.  There was a steady stream of reports of students being arrested or harassed by police after they had been found trespassing or had been accused of stalking.  While the actions of these student reporters departed from what Tweedie had intended, it told him something important: the will to peel back the layers of secrecy and deceit that crippled the public's understanding of major events, long thought to be lost on the young generations of the 21st century, was alive and well.

@@

When William Tweedie had announced his pet program for reinvigorating investigative journalism, he had personally notified Jesse that his job description would be changing.  If he felt comfortable with the plan, then he was welcome to stay.  Jesse was intrigued by the promise of hush-hush work, additional travel, and doing his part to promote an old component of journalism that he had found lacking.  He signed a non-disclosure agreement, agreed to the revised terms, and came to work the next week to find that his desk and computer had been removed.  In its place was a note from the dean and a plane ticket without a marked destination that left from a terminal at JFK that Jesse had  never heard of.  ``This should be educational,'' he said, turning on his heel and heading toward the elevator.

``You're going to eastern Europe,'' the dean had told him.  ``The flight plan has been filed, and your pilot knows what to do.  Here's some background for you to read over while you're over the Atlantic.''  He handed Jesse a thin tablet computer whose only marking was a serial number etched into the upper right corner.

``What's the scoop?'' Jesse asked, running his hand over the tablet.

``You'll find everything on there,'' said the dean.  ``This project is the president's baby, and you probably know more than I do.  When you land, use the switch on the side of the tablet to securely erase its flash memory.  None of the information on it is illegal, but it's sensitive and we don't want you getting tied up in a rumble with immigration.''

``All right,'' Jesse said.  He noted the location of the secure erasure switch and looked back at the dean.  ``Should I pay an extra month's rent, or is this a visit for tea?''

The dean laughed.  ``See you in two weeks, son.''

\chapter{}

@@

``Don't worry, the bottoms are magnetic,'' Milssen said, gently tipping his own mug from side to side to show the resistance of the magnet.  ``One of the perks of these corporate birds.''

@@

``Ready for duty?'' Milssen asked with a smile.

``Not a chance,'' Jesse said, ``but I'll do what I can.  These kids really stepped in it.''

``The bits of news that have made it to my ear haven't been good.  Be careful, and we'll see you Thursday evening.  Give me a call when you're packed up.  We'll be starting our descent in about twenty.''

@@

Jesse knew that tomorrow, Wednesday, would be a tense affair.  He kept his nerves hidden, but his bowels never got the memo.  \emph{I won't be doing this until I retire, unless they let me go at 32}, he thought, looking out the tiny window at the hills of central Europe.

The kids had \emph{really} stepped in it.  One student, the son of Polish immigrants, had enrolled in the new investigative journalism program at CUNY with a personal mission to prove that his father's failed bid for a seat on the Warsaw City Council in 1986 had been illegally sabotaged.  The family was convinced that an opponent had floated a rumor about his father's marital fidelity shortly before the election, and that another political rival had abused her position of power at town meetings as a soapbox for making inaccurate statements about the family's intentions.  The student, Sam Rzeznik, had recruited two of his classmates to join him in Poland for a month to investigate the case.

The true story, however, had only come to light after the team of students was arrested by Interpol for breaking into the offices of a local political party and installing recording devices.  The official application for funds had stated that the team would be investigating instances of polling irregularities at a handful of small voting precincts outside of Warsaw.  The low-key nature of the trip, and the delicate issue at hand, had won over the review board and brought praise from William Tweedie.  The team had been awarded a travel and research grant for \$8,000, enough to keep them fed and mobile for 30 days.

@@

\chapter{}

@@

``Jesse Winter?'' the man said.  His voice was clear despite an accent that Jesse couldn't place, but the accent didn't concern him as much as the lack of friendliness.  Jesse reminded himself that he shouldn't expect to make friends today.  \emph{Time to go to work}.

``Pleased to meet you.  Mr...?'' Jesse said, offering his hand.

The man stood up, shaking Jesse's hand.  ``Jasna.  Marcel Jasna.  You may call me Marcel.  May I call you Jesse?''

``Sure,'' Jesse said.

``Shall we sit, then?'' said Marcel, gesturing to the empty chair across the small table.

@@

``Well, Jesse, it's no secret why we come here today,'' Marcel said simply.  ``The manager of my brother's political office caught your students in his building.  It was clear to us that they were spying on our meetings and attempting to sabotage our campaign.  We have video and audio evidence from the night when they entered the building and left recording devices.  This is, as you say, an open and shut case, don't you think?''

Jesse opened his mouth to respond, but Marcel had paused only for rhetorical effect.  He went on: ``My brother has no interest in ruining the lives of young people.  But he finds your program that encourages students to become foreign spies for the United States to be distasteful and shameful.  If students go to jail for a time in order to bring the proper shame on your program, very few Polish citizens here will pay attention.  Your program is unpopular in your own country, yes?''

This time Marcel stopped to wait for a response, but Jesse sensed a trap.  ``The program enjoys strong support from many quarters,'' he offered.

``Yes, there are always those who see public servants as corrupt by definition.  Have you noticed that foreign politicians are always corrupt, but your government does not look at its own face in a mirror?''  Marcel took a drink from his glass, then cleared his throat.  ``This is not so simple as you think, Jesse.  You are thinking of your students, their future, their families, your president, perhaps your job.  We understand that it is far deeper.  Each time our politicians are painted as corrupt, Poland suffers.  We have suffered under the heel of such injustice for most of a century.''

Jesse shifted in his seat.  ``Marcel, these students lied to us.  I understand your position on spying, and I know that from your vantage point we seem to be training a new crop of young spies.  You need to know that these students were not authorized to conduct themselves in this way.  They lied on the application, and they lied to the review committee.''

``This does not change substance of the situation.''

``That's correct.  But it changes the details of the situation that you and I care about.  We're not here to debate state philosophies on espionage.  This is about the welfare of a group of kids who, while they showed themselves to be overzealous, have passion and talent that \emph{must} be put to productive uses.  Do you see?''

Marcel responded immediately.  ``With respect, the fate of the students is beside the point.  This is an issue of national and political sovereignty, and we intend to treat it as such.  I must admit that I do not think we will reach a settlement.  We must not appear weak in the face of interference from America, even if the face is that of a young spy ring.''

@@

``Our university is prepared to work with you, sir,'' Jesse continued.  ``We have no interest in inflaming the relationship between the U.S. and a friendly nation such as Poland.  We know that despite your feelings about espionage, it would not bode well for your campaign to be associated with the arrest of a Polish student.''  Turning his palms upward in a conciliatory gesture, Jesse added, ``What options remain on the table?''

Marcel leaned back in his seat and tilted his head to the right, clearly wondering what Jesse had been in Jesse's mind as he spoke those words.  It was a moment before he spoke again.  ``You offer us money, Jesse?''

``We are prepared to cover the costs of the repairs to your brother's office, as well as any legal costs that you've absorbed.  Beyond that, well . . . this is a negotiation.''

``Please excuse me for a moment, Jesse,'' Marcel said, rising to his feet and walking toward the back door of the cafe.

\emph{Time for a side-conference during the powwow}, Jesse thought to himself.  He took the moment to enjoy a taste of the gin and tonic in front of him that had so far been ignored.  As the strong flavor filled his senses, Jesse talked himself through the next few minutes of his conversation.  The man in the other chair suspected that Jesse was out of chips in the negotiation.  Jesse was certain of that.  Jesse also knew that his own case was weak and that offering money for repairs and cooperation was small potatoes to these guys.  Someone who cares about national and political sovereignty wasn't going to let a group of foreign kids with an agenda go without making a point or making some demands to make the American politians squirm.  And Jesse was just a pawn in all of this.  He knew that Marcel felt no personal sympathy for him.

@@

``My apologies, Jesse,'' Marcel said as he took his seat.  ``My brother can be very detailed.''

``Not to worry.  How is he doing?''

``Very busy these days.  This issue with the students has taken a lot of his time, and he is eager to wash his hands of them.''

\emph{Didn't expect that}, Jesse thought.  \emph{But he's not finished}.

``However,'' Marcel said, leaning back in his seat and slowly turning his glass, ``a detail has come to his attention today.  One of the students, Sam Rzeznik.  You know of him?''

@@

``Yes,'' Marcel continued.  ``It seems that his family has a history.  A history that complicates things for us.  What do you know about this?''

``I know that Sam is of Polish descent,'' Jesse said.  ``He mentioned in his interview with our review board that his grandfather was a public servant, but no serious problems came up during the proceedings.  Everything that Sam told us was verified before he was allowed to start his research project.''

That much was true, but Jesse wasn't revealing his hand just yet.  The political problems had not involved Sam's grandfather, who had been involved in municipal government for most of his life.  Sam's father, on the other hand, had found himself the victim of circumstances entirely beyond his control.  The review board that CUNY had convened to consider the applications submitted by the investigative journalism students had learned about Jesse's father's political past after conversing with Polish authorities, but the board had given its stamp of approval after reviewing the facts.

``Yes, his grandfather served in the city government with my grandfather.  Those were very good days for Poland, despite the problems of the world.  It was the next generation that began the divisive era of our politics that we still see today.  The dishonesty.  The posturing.''  Marcel paused, looking pointedly at Jesse.  ``And the \emph{spying}.  It is this generation that Sam's father helped to assemble.

``My father was in his third year on the city council when Sam's father declared himself a candidate for the same seat.  My father had worked for ten years to clean up this city, and to restore pride to Warsaw citizens.  He had done every task to match the letter of the law.  His constituents trusted him.  Sent him letters of thanks each year.  He knew the spirit of the people, and knew how to bring money and business to Warsaw.  He understood the real purpose of a public life.''

Marcel took a deep breath, clearly incensed by the memories that he was bringing to mind.  ``When Sam's father declared himself a candidate, he . . . he knew nothing of politics.  He knew nothing of campaigns.  His only public achievement was to manage the local library, and poorly at that.  The library was never lower on funds.  He began to attend city council meetings, asking impossible questions.  There was never a more irritating man.  He knew nothing of the business of government, but he made it his mission to lecture everyone on what he called the `proper order of the gathering'.

``It was known that he saw visited women other than his wife.  After he declared his candidacy, this secret became known to the public.  It is not clear how this information became known.  He never recovered from the stain on his reputation, and he lost the election.  It was soon after that his family left the country, and we see now that he reaches through his son in an attempt to blame us for his past mistakes.''

Marcel paused to finish his scotch.  ``There will be no deal, Jesse.''

``Are you familiar with the phrase `catch-22', Marcel?''

``Yes, of course.  It is a situation in which every available course of action carries negative consequences.  Why do you ask this?''

``Since you are familiar with your father's political story, you might remember an incident involving an old woman in June of 1986.''

Marcel's face clouded, and he shifted in his seat.  ``Yes,'' he allowed, ``I am familiar.''

``If I told you that we had an voice record of that conversation, would this change the substance of our discussion?''

@@

Marcel considered Jesse for a long moment.  ``You attempt to deceive me.''

``It is not your claims, sir, but the way that you abuse the trust of the people with one hand while smoothing their feathers with the other that make me doubt you,'' Jesse said, making it clear that he was uttering a quotation.  The old woman had spoken with an east Warsaw accent.

Marcel stared at him.  He would have remembered that decades-old quote.  Just when Jesse was sure that he had collected his thoughts and had worked out a stinging train of logic, he took a deep breath and pulled a cash clip from his pocket.  He placed three Euro notes on the table before replacing the clip in his trousers.  Then he met Jesse's eyes.

``Your students will meet you at the airport tomorrow, Mr. Winter,'' Marcel said.

Marcel was out of his seat and halfway to the door of the cafe before Jesse fully processed what had happened.  The students were absolved of their legal worries.  An impossible situation had been turned on its head.  But there was no way that this was the end of the story.  These guys didn't quit that easily.  Jesse's trump card had ended the contest, but he knew that he would hear from Marcel again before he retired.  \emph{Unless I retire at 32}.

@@

``Mr. Jesse Winter?'' the officer asked, glancing at a sheet of paper in his hand and looking back at Jesse.

``Yes?'' Jesse replied.

``I'm detective Morse from the CUNY police department, I'd like to ask you a few questions, if that's all right.''

``Certainly.  Please come in.''  \emph{This should be good}, Jesse thought, feeling his pulse quicken.

The officer stood near the door, refusing Jesse's offer of a chair.  ``Mr. Winter,'' he said, ``one of the members of the board of directors has launched an investigation into your involvement in the Warsaw incident from June.  Are you familiar with that case?''

``Yes, I traveled to Poland in June to negotiate on behalf of the university.  What's this about?''

``Would you mind coming down to the station to talk about it?  We can be sure of our privacy there.''

``Am I under arrest, detective?''

``No, sir.  We just want you to discuss a few things with us.''

``This office is private.  Why not stay here?''  Jesse felt his old privacy hackles starting to rise.  \emph{My office is certainly more private than an interrogation room}.

``With all due respect, Jesse, given your involvement in this case you should know better than to assume something like that.''

@@

The case against Jesse was surprisingly weak, but the university prosecutor had constructed an elaborate argument that had a chance of succeeding.  If he could convince the judge that Jesse had issued a threat, even an implied one, then Jesse could be found guilty of obstruction of justice.  His attorney seemed confident that the judge would reject the argument, but its plausibility made Jesse nervous.  If the key question was whether Jesse issued a threat, then he was in a difficult position.  He \emph{had} issued a threat, although it was not spoken.  Anyone who had been privy to the conversation in Warsaw would have understood that what Jesse said was a threat.  But the thing gnawing at Jesse's mind was how that information had made its way to the ear of one of the board members.  One of two things was true.  Either Rheingold had secured a copy of the documents on the tablet computer that Jesse had carried to Warsaw, or Marcel and his brother had made a contact in the United States.  The latter worried Jesse on a much deeper level than the former.

@@

``Will the defendant please rise?'' the judge drawled.

@@

``In the case of Rheingold versus Winter, we find the defendant not guilty on the charges of obstruction of justice.  Mr. Winter, you are free to leave.''  After a brief pause, the judge cleared his throat and added: ``Off the record, I think that this case was a poor use of the court's time.  Good day, gentlemen.''

@@

``Good show, Jesse,'' Sascha Greene said with a wink.
